cardinalR: Generating interesting high-dimensional data structures

### 2025-09-19 paper-cardinalR.Rmd
Added overview paragraph for shape generators

>>>>

The shape generators form the foundation of the package, providing a collection of functions to create synthetic data structures based on simple, well-defined geometric structures. These include fundamental shapes such as cones, pyramids, spheres, grids, and branching structures. If a shape is not inherently defined in more than three dimensions, additional noise dimensions can be added to embed the structure into higher-dimensional space. Users can specify how these noise dimensions are generated (e.g., Gaussian, uniform), offering control over the embedding process. All shape generators allow the user to define the number of points and dimensions, and most include additional arguments to customize specific characteristics of the structure.
